Discrete Quantum Theories and Computing

### 2018-11-21 dissertation.tex
dissertation.lyx "2.2.1 Classical and Quantum Probability Spaces" Updating...

One special feature of quantum experiments is that the probabilities
in different experiments are correlated. Consider another experiment
similar to the previous one. While sending exactly the same particle,
we use a different beam splitter corresponding to the observable $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
Now the sample space is $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $,
and another probability measure $\mu_{1}:2^{\Omega_{1}}\rightarrow\left[0,1\right]$
is defined. Although the sample spaces and the probability measures
are different, these two experiments may produce the same outcome
state~$\ket{2}$, and the probability of the common event $\left\{ \ket{2}\right\} $
is experimentally found to be the same, i.e., $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
In general, as long as sending the same particle, the probability
of the same event in different experiments are always the same. This
fact is equivalent to the fact that commuting observables could be
measured simultaneously, and the latter fact is essential to define
contextuality which will be explained later.

Since the probability induced by the different beam splitters are
correlated, it is more natural to define the set of quantum events~$\events$
as the union of all possible event spaces using different beam splitters.
Because we are focus on the probability instead of outcome, and the
probabilities of events $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
are always the same, it is reasonable to identify them as the same
event. By observing the projectors generated by these two events are
the same
\begin{equation}
\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}\,,
\end{equation}
we define the projector generated by any classical event~$E$ as
its quantum event 
\begin{equation}
\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\in\events\,.\label{eq:pullback-function}
\end{equation}
If we follow the convention $\varphi\left(\emptyset\right)=\mathbb{0}$,
not only the events mapping to the same projector must have the same
probability, but this function $\varphi$ also naturally sends the
set structure to the corresponding projector structure: $\varphi\left(\Omega\right)=\mathbb{1}$
and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
Given a sample space $\Omega$ and a pair of event $E_{0}\subseteq\Omega$
and $E_{1}\subseteq\Omega$, their corresponding quantum events $\varphi\left(E_{0}\right)$
and $\varphi\left(E_{1}\right)$ are commuting and vice versa, where
two projectors $P_{0}$ and~$P_{1}$ are \emph{commuting} if $P_{0}P_{1}=P_{1}P_{0}$.
Moreover, the events $E_{0}$ and $E_{1}$ in the same sample space
also satisfy the following properties: 
\begin{align}
\varphi\left(E_{0}\cap E_{1}\right) & =\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,, & \varphi\left(E_{0}\cup E_{1}\right) & =\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,.\label{eq:pullback-properties}
\end{align}
If $E_{0}$ and $E_{1}$ are disjoint, then $\varphi\left(E_{0}\right)$
and $\varphi\left(E_{1}\right)$ are orthogonal and vice versa, where
two projectors $P_{0}$ and $P_{1}$ are called \emph{orthogonal}
if $P_{0}P_{1}=\mathbb{0}$.

>>>>

One special feature of quantum experiments is that the probabilities
in different experiments are correlated. Consider another experiment
similar to the previous one. While sending exactly the same particle,
we use a different beam splitter corresponding to the observable $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
Now the sample space is $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $,
and another probability measure $\mu_{1}:2^{\Omega_{1}}\rightarrow\left[0,1\right]$
is defined. Although the sample spaces and the probability measures
are different, these two experiments may produce the same outcome
state~$\ket{2}$, and the probability of the common event $\left\{ \ket{2}\right\} $
is believed to be the same, i.e., $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
In general, as long as sending the same particle, the probability
of the same event in different experiments are always the same. This
fact is equivalent to the fact that commuting observables could be
measured simultaneously, and the latter fact is essential to define
contextuality which will be explained later.

Since the probability induced by the different beam splitters are
correlated, it is more natural to define one quantum event space~$\events$
containing all possible event spaces using different beam splitters.
However, a simple union of all event spaces will contain duplicate
information. For example, if we take the complement on the both sides
of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
we will have
\begin{equation}
\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
\end{equation}
that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same as
well. To simplify our discussion, it might be desirable to identify
two classical events $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
as one quantum event. Fortunately, the projectors generated by these
two events are the same, i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$.
Thus, given a classical event~$E$, we may define its corresponding
quantum event $\varphi\left(E\right)$ as the projector generated
by $E$,
\begin{equation}
\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
\end{equation}
with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$. Then,
a quantum event space $\events$is the set of all projectors on a
given Hilbert space.

It is easy to check that defining quantum

we not only want to consider all possible events with different beam
splitters as a whole, but also want to

Because the projectors generated by these two events are the same,
i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$,

if we want to consider all possible events with different beam splitters
as a whole, it might be easier to define a quantum

we could simplify our discussion by mapping a classical event~$E$

To simplify our discussion on quantum probability, it would be better
to identify $\left\{ \ket{0},\ket{1}\right\} $ and $\left\{ \ket{\ps},\ket{\ms}\right\} $
as the same event. Fortunately, the projectors generated by these
two events are the same, i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$.
So does

Because we are focus on the probability instead of outcome,

Since the probability induced by the different beam splitters are
correlated, it is more natural to define the set of quantum events
as the union of all possible event spaces using different beam splitters.
Because we are focus on the probability instead of outcome, and ,
it is reasonable to identify them as the same event. By observing
the projectors generated by these two events are the same, i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$,
we define the projector generated by any classical event~$E$ as
its quantum event

It is easy to verify that , not only the events mapping to the same
projector must have the same probability, but this function $\varphi$
also naturally sends the set structure to the corresponding projector
structure: $\varphi\left(\Omega\right)=\mathbb{1}$ and $\varphi\left(\overline{E}\right)=\mathbb{1}-\varphi\left(E\right)$.
Given a sample space $\Omega$ and a pair of event $E_{0}\subseteq\Omega$
and $E_{1}\subseteq\Omega$, their corresponding quantum events $\varphi\left(E_{0}\right)$
and $\varphi\left(E_{1}\right)$ are commuting and vice versa, where
two projectors $P_{0}$ and~$P_{1}$ are \emph{commuting} if $P_{0}P_{1}=P_{1}P_{0}$.
Moreover, the events $E_{0}$ and $E_{1}$ in the same sample space
also satisfy the following properties: 
\begin{align}
\varphi\left(E_{0}\cap E_{1}\right) & =\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,, & \varphi\left(E_{0}\cup E_{1}\right) & =\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,.\label{eq:pullback-properties}
\end{align}
If $E_{0}$ and $E_{1}$ are disjoint, then $\varphi\left(E_{0}\right)$
and $\varphi\left(E_{1}\right)$ are orthogonal and vice versa, where
two projectors $P_{0}$ and $P_{1}$ are called \emph{orthogonal}
if $P_{0}P_{1}=\mathbb{0}$.
